---
title: "penn_Munging"
author: "Jake Eisaguirre"
date: "2022-08-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

# librarian downloads, if not already downloaded, and reads in needed packages

librarian::shelf(tidyverse, here, janitor, lubridate, parsedate, stringr,hms, DBI, RPostgres)
```

#### read in capture data
```{r}

munged_Amphibian_Processing_App <- read_csv(here("data", "munged_Amphibian_Processing_App.csv"))

munged_Amphibian_Captured_Information <-  read_csv(here("data", "munged_Amphibian_Captured_Information.csv"))
                       
munged_Amphibian_Captured_Information_Repeatable <- read_csv(here("data", "munged_Amphibian_Captured_Information_Repeatable.csv"))

munged_Amphibian_Processing_App_Repeatable <- read_csv(here("data", "munged_Amphibian_Processing_App_Repeatable.csv"))
```

#### read in visual data
```{r}

munged_VisualEncounter_Survey <- read_csv(here("data", "munged_VisualEncounter_Survey.csv"))
  
munged_VisualEncounter_Survey_Repeatable <- read_csv(here("data", "munged_VisualEncounter_Survey_Repeatable.csv"))

```

#### read in acoustic data
```{r}

munged_Acoustic_Survey <- read_csv(here("data", "munged_Acoustic_Survey.csv"))

munged_Acoustic_Survey_Repeatable <- read_csv(here("data", "munged_Acoustic_Survey_Repeatable.csv"))

```


#### merge all capture tables - bad technique, too many pipes
```{r}

  
merged_AmphibianCaptureSurvey <- right_join(right_join(munged_Amphibian_Captured_Information,
                                                        munged_Amphibian_Captured_Information_Repeatable, 
                                                        by = c("fulcrum_id" = "fulcrum_parent_id")),
                                            right_join(munged_Amphibian_Processing_App,
                                                       munged_Amphibian_Processing_App_Repeatable, 
                                                       by =c('fulcrum_id' = 'fulcrum_parent_id')),
                                            by = c('location', 'date', 'bag_id')) %>% 
  select(!c( "fulcrum_id.x", "created_at.x.x", "fulcrum_id.y.x", "created_at.y.x", 
            "fulcrum_id.y.y", "created_at.x.y", "fulcrum_id.y.y.y","created_at.y.y", "time_of_capture.y", 
            "body_temperature.y", "microhabitat_type.y","microhabitat_temperature.y", "observer_other", "processor_other",
            "capture_type_other", "sex_other", "species")) %>% 
  rename(survey_comment = survey_comments.x,
         visit_comment = survey_comments.y,
         time_of_capture = time_of_capture.x,
         body_temperature_c = body_temperature.x,
         microhabitat_type = microhabitat_type.x,
         microhabitat_temperature_c = microhabitat_temperature.x,
         site = location) %>% 
  mutate(date = parse_date(date),
         observer = str_to_lower(observer),
         site = str_to_lower(site),
         bag_id = str_to_lower(bag_id),
         microhabitat_type = str_to_lower(microhabitat_type),
         processor = str_to_lower(processor),
         capture_type = str_to_lower(capture_type),
         life_stage = str_to_lower(life_stage),
         species_capture = str_to_lower(species_capture),
         sex = str_to_lower(sex)) %>% 
  unique() %>% 
    mutate(start_hour = hour(start_time),
         end_hour = hour(end_time),
         survey_time = case_when(start_hour >= 6 & end_hour >= 6 & end_hour < 19 ~ "day", 
                          start_hour >= 19 &  (end_hour < 6 | end_hour <= 23) |
                         (start_hour < 6 & end_hour < 6)~ "night",
                         start_hour >=19 ~"night")) %>% 
  select(!c(start_hour, end_hour)) %>% 
  mutate(species_capture = paste(species_capture, species_capture_other, sep = ""),
         species_capture = str_replace(species_capture, "NA", ""),
         region = "pa",
         location = "usa",
         detection_type = "capture") %>% 
  select(!c(species_capture_other))%>% 
  mutate(survey_time = if_else(is.na(survey_time), "night", survey_time))


```

#### pull out locatoin and region table
```{r}
location <- merged_AmphibianCaptureSurvey %>% 
  select(location) %>% 
  unique() %>% 
  write_csv(here("clean_tables", "location.csv"))

region <- merged_AmphibianCaptureSurvey %>% 
  select(region) %>% 
  unique() %>% 
  write_csv(here("clean_tables", "region.csv"))
```


#### pull out capture site table
```{r}

cap_site_table <- merged_AmphibianCaptureSurvey %>% 
  select(location, region, site, date, observer)

```

#### pull out capture visit table
```{r}

cap_visit_table <- merged_AmphibianCaptureSurvey %>% 
  select(date, survey_time, site, visit_comment, detection_type) %>% 
  mutate(visit_comment = str_to_lower(visit_comment))

```

#### pull out capture survey table
```{r}

cap_survey_table <- merged_AmphibianCaptureSurvey %>% 
  select(site, date, observer, detection_type, start_time, end_time, survey_comment, survey_time) %>% 
  mutate(duration_min = if_else(end_time < start_time,
                            as_hms(86400) - start_time + end_time,
                            end_time - start_time),
         duration_min = duration_min/60,
         survey_comment = str_to_lower(survey_comment)) %>% 
  relocate(survey_comment, .after = duration_min) 

cap_survey_table$duration_min <- str_sub(cap_survey_table$duration_min, -4) %>% 
  as.numeric()



```

#### pull out cap animal table
```{r}
cap_animal <- merged_AmphibianCaptureSurvey %>% 
  mutate(capture_type = if_else(is.na(capture_type), "new", capture_type)) %>% 
  select(c(bag_id:detection_type, site, date)) %>% 
  mutate(capture_comments = str_to_lower(capture_comments),
         bd_swab_tube_id = if_else(bd_swab_tube_id == "BdSwab00000", "NA", bd_swab_tube_id),
         dry_swab_tube_id=if_else(dry_swab_tube_id == "DrySwab00000", "NA", dry_swab_tube_id),
         crispr_swab_tube_id=if_else(crispr_swab_tube_id == "CRSwab00000", "NA", crispr_swab_tube_id),
         bacterial_swab_tube_id=if_else(bacterial_swab_tube_id == "BacSwab00000", "NA", bacterial_swab_tube_id),
         mucusome_id=if_else(mucusome_id == "MucBath00000", "NA", mucusome_id),
         amp_id_1=if_else(amp_id_1 == "AMPBath00000", "NA", amp_id_1),
         amp_id_2=if_else(amp_id_2 == "AMPBath00000", "NA", amp_id_2),
         amp_id_3=if_else(amp_id_3 == "AMPBath00000", "NA", amp_id_3),
         amp_id_4=if_else(amp_id_4 == "AMPBath00000", "NA", amp_id_4),
         antibody_id_1=if_else(antibody_id_1 == "AntiBod00000", "NA", antibody_id_1),
         antibody_id_2=if_else(antibody_id_2 == "AntiBod00000", "NA", antibody_id_2),
         antibody_id_3=if_else(antibody_id_3 == "AntiBod00000", "NA", antibody_id_3),
         antibody_id_4=if_else(antibody_id_4 == "AntiBod00000", "NA", antibody_id_4),
         toe_clip_tube_id=if_else(toe_clip_tube_id == "ToeClip00000", "NA", toe_clip_tube_id))%>% 
   mutate(temp_ves_id = 1:n()) %>% 
  unite(life_stage, life_stage:life_stage_other, sep = "", na.rm = T)
```

# add cmr id to animal table
```{r}
cmr <- read_csv(here("data", "munged_CMR_Data.csv"))
  
cc <- cmr %>% 
  unite(cmr_id, cmr_id:cmr_id_other, sep="", na.rm=T)


# remove duplicate cmr data
dups <- cc %>% 
  group_by(fulcrum_id) %>% 
  mutate(dub_id = cur_group_id()) %>% 
  ungroup() %>% 
  mutate(temp_id = 1:n())

to_remove <- c(82, 83, 81, 80, 84, 78, 79)


cmr_noDups <- dups %>% 
  na_if("") %>% 
  filter(!temp_id %in% to_remove) %>% 
  drop_na(cmr_id) %>% 
  select(!c(temp_id, dub_id))

# join cmr id (toe clip number) to all animal capture data to know which toes have been clipped initiall and be able to id if recap
cap_animal_table_cmr_id <- cap_animal %>%
  left_join(cmr_noDups, by = c("capture_mark_recapture" = "fulcrum_id")) %>% 
  select(!c(capture_date, species, location.y, temp_ves_id, created_at))

# pull out frogs who have been recaptured
re_cap_table <- cap_animal_table_cmr_id %>% 
  filter(capture_type == "recapture") %>% 
  drop_na(capture_mark_recapture)

colnames(re_cap_table) <- paste(colnames(re_cap_table), "recap", sep="_")

# pull out frogs that are new captures
cap_animal_table <- cap_animal_table_cmr_id %>%
  filter(capture_type == "new")

# look for duplicates
test_dubs <- re_cap_table %>% 
  drop_na(cmr_id_recap) %>% 
  group_by(site_recap, species_capture_recap, cmr_id_recap) %>% 
  mutate(temp_id = cur_group_id()) %>% 
  filter(duplicated(temp_id))


write_csv(cap_animal_table, here("clean_tables", "capture.csv"))
write_csv(re_cap_table, here("clean_tables", "recapture.csv"))
```

### re-catpures table
```{r}

re_cap_table <- cap_animal %>% 
  filter(capture_type == "recapture")





```


#### merge visual tables
```{r}
merged_VisualEncounterSurvey <-
left_join(munged_VisualEncounter_Survey, munged_VisualEncounter_Survey_Repeatable, by = c('fulcrum_id' = 'fulcrum_parent_id')) %>% 
  select(observer, date, location, start_time, end_time, species_ves, count_ves, comments_ves) %>%
  unique() %>%
  drop_na(species_ves) %>% 
  mutate(observer = str_to_lower(observer),
         date = parse_date(date),
         location = str_to_lower(location),
         species_ves = str_to_lower(species_ves),
         comments_ves = str_to_lower(comments_ves)) %>% 
  rename(count = count_ves,
         site = location) %>% 
      mutate(start_hour = hour(start_time),
         end_hour = hour(end_time),
         survey_time = case_when(start_hour >= 6 & end_hour >= 6 & end_hour < 19 ~ "day", 
                          start_hour >= 19 &  (end_hour < 6 | end_hour <= 23) |
                         (start_hour < 6 & end_hour < 6)~ "night",
                         start_hour >=19 ~"night"),
         region = "pa",
         location = "usa",
         detection_type = "visual") %>% 
  select(!c(start_hour, end_hour))%>% 
  mutate(survey_time = if_else(is.na(survey_time), "night", survey_time),
         site = if_else(is.na(site), "phelps pond", site))

```

#### pull out visual site table
```{r}

visual_site_table <- merged_VisualEncounterSurvey %>% 
  select(location, region, site, date, observer)

```

#### pull out visual visit table
```{r}

visual_visit_table <- merged_VisualEncounterSurvey %>% 
  select(date, survey_time, site, detection_type)

```


#### pull out visual survey table
```{r}

visual_survey_table <- merged_VisualEncounterSurvey %>% 
  select(site, date, observer, detection_type, start_time, end_time, detection_type, survey_time) %>% 
  mutate(duration_min = if_else(end_time < start_time,
                            as_hms(86400) - start_time + end_time,
                            end_time - start_time),
         duration_min = duration_min/60) %>% 
  relocate(detection_type, .after = duration_min)

visual_survey_table$duration_min <- str_sub(visual_survey_table$duration_min, -4) %>% 
  as.numeric()

```

#### pull out visual animal table
```{r}

visual_animal_table <- merged_VisualEncounterSurvey %>% 
  select(date, site, species_ves, count, comments_ves, survey_time, detection_type) %>% 
   mutate(temp_ves_id = 1:n()) %>% 
  select(!c(temp_ves_id))

write_csv(visual_animal_table, here("clean_tables", "visual.csv"))

```


#### merge acoustic tables
```{r}

merged_AcousticSurvey <-
left_join(munged_Acoustic_Survey, munged_Acoustic_Survey_Repeatable, by = c('fulcrum_id' = 'fulcrum_parent_id')) %>%
  select(observer, date, location, start_time, end_time, species_acoustic, call_index, acoustic_comments) %>%
  unique() %>%
  mutate(observer = str_to_lower(observer),
         date = parse_date(date),
         location = str_to_lower(location),
         species_acoustic = str_to_lower(species_acoustic),
         call_index = str_to_lower(call_index),
         acoustic_comments = str_to_lower(acoustic_comments)) %>% 
  rename(site = location) %>% 
  mutate(duration_min = if_else(end_time < start_time,
                            as_hms(86400) - start_time + end_time,
                            end_time - start_time),
         duration_min = duration_min/60,
         detection_type = "acoustic",
          region = "pa",
         location = "usa",
         start_hour = hour(start_time),
         end_hour = hour(end_time),
         survey_time = case_when(start_hour >= 6 & end_hour >= 6 & end_hour < 19 ~ "day", 
                          start_hour >= 19 &  (end_hour < 6 | end_hour <= 23) |
                         (start_hour < 6 & end_hour < 6)~ "night",
                         start_hour >=19 ~"night")) %>%
  relocate(duration_min, .before = species_acoustic)

merged_AcousticSurvey$duration_min <- str_sub(merged_AcousticSurvey$duration_min, -4) %>% 
  as.numeric()
  
```

#### pull out acoustic site table
```{r}

acoustic_site_table <- merged_AcousticSurvey %>% 
  select(location, region, site, date, observer)

```

#### pull out acoustic visit table
```{r}

acoustic_visit_table <- merged_AcousticSurvey %>% 
  select(date, survey_time, site, detection_type)

```

#### pull out acoustic survey table
```{r}

acoustic_survey_table <- merged_AcousticSurvey %>% 
  select(site, date, observer, detection_type, start_time, end_time, duration_min, detection_type, survey_time)
  

```

#### pull out acoustic animal table
```{r}

acoustic_animal_table <- merged_AcousticSurvey %>% 
  select(date, site, species_acoustic, call_index, acoustic_comments, survey_time, detection_type) %>% 
   mutate(temp_ves_id = 1:n()) %>% 
  select(!c(temp_ves_id))

write_csv(acoustic_animal_table, here("clean_tables", "acoustic.csv"))

```

#### bind all site tables for uniquness
```{r}

site_table <- rbind(acoustic_site_table, visual_site_table, cap_site_table) %>% 
  group_by(site) %>% 
  mutate(temp_reg_id = cur_group_id()) %>% 
  filter(!duplicated(temp_reg_id)) %>% 
  select(!c(temp_reg_id))

write_csv(site_table, here("clean_tables", "site.csv"))

```



#### bind all visit table for uniquness
```{r}

visit_table <- plyr::rbind.fill(acoustic_visit_table, visual_visit_table, cap_visit_table) %>% 
  group_by(date, survey_time, site) %>% 
  mutate(temp_reg_id = cur_group_id()) %>% 
  filter(!duplicated(temp_reg_id)) %>% 
  select(!c(temp_reg_id))

write_csv(visit_table, here("clean_tables", "visit.csv"))

```

#### bind all survey table for uniquness
```{r}

survey_table <- plyr::rbind.fill(acoustic_survey_table, visual_survey_table, cap_survey_table) %>% 
  group_by(date, site, detection_type, survey_time) %>% 
  mutate(temp_reg_id = cur_group_id()) %>% 
  filter(!duplicated(temp_reg_id)) %>% 
  select(!c(temp_reg_id))

write_csv(survey_table, here("clean_tables", "survey.csv"))

```

#### connect to local db
```{r}
tryCatch({
    drv <- dbDriver("Postgres")
    print("Connecting to Database…")
    connection <- dbConnect(drv, 
                 dbname = Sys.getenv("dbname"),
                 host = Sys.getenv("host"), 
                 port = Sys.getenv("port"),
                 user = Sys.getenv("user"), 
                 password = Sys.getenv("password"))
    print("Database Connected!")
    },
    error=function(cond) {
            print("Unable to connect to Database.")
    })

dbExecute(connection, "set search_path to pennsylvania")
```

#### load tabltes
```{r}
#location table load
dbWriteTable(connection, 'location', location, overwrite=T)

#region table load
dbWriteTable(connection, 'region', region, overwrite=T)

#site table load
dbWriteTable(connection, 'site', site_table, overwrite=T)

#visit table load
dbWriteTable(connection, 'visit', visit_table, overwrite=T)

#survey table load
dbWriteTable(connection, 'survey', survey_table, overwrite=T)

#aural table load
dbWriteTable(connection, 'aural', acoustic_animal_table, overwrite=T)

#capture table load
dbWriteTable(connection, 'capture', cap_animal_table, overwrite=T)

#recapture table load
dbWriteTable(connection, "recapture", re_cap_table, overwrite=T)

#visual table load
dbWriteTable(connection, 'visual', visual_animal_table, overwrite=T)

```


